### 2024-01-01 docs/projects/data-formats/hdf/index.qmd
rerendered documents in new Clay version (corrected source links, changed table styling)

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default3.js" type="text/javascript"></script><script src="index_files/md-default4.js" type="text/javascript"></script>
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>

@@

<div><pre><small><small>source: /home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-formats/hdf/notebooks/index.clj</small></small></pre></div>

>>>>

---
<style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default3.js" type="text/javascript"></script><script src="index_files/md-default4.js" type="text/javascript"></script>
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>

@@

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/data-formats/hdf/notebooks/index.clj">projects/data-formats/hdf/notebooks/index.clj</a></small></small></pre></div>

### 2024-01-01 docs/projects/visual-tools/clay-calva-demo-20231216/index.qmd
rerendered documents in new Clay version (corrected source links, changed table styling)

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default1.js" type="text/javascript"></script><script src="index_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="index_files/vega3.js" type="text/javascript"></script><script src="index_files/vega4.js" type="text/javascript"></script><script src="index_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>

>>>>

---
<style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default1.js" type="text/javascript"></script><script src="index_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="index_files/vega3.js" type="text/javascript"></script><script src="index_files/vega4.js" type="text/javascript"></script><script src="index_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>

### 2024-01-01 docs/projects/visual-tools/clay-cider-demo-20231217/index.qmd
rerendered documents in new Clay version (corrected source links, changed table styling)

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default13.js" type="text/javascript"></script><script src="index_files/md-default14.js" type="text/javascript"></script>
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>

>>>>

---
<style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default13.js" type="text/javascript"></script><script src="index_files/md-default14.js" type="text/javascript"></script>
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
